External validation

### 2019-12-11 diagnostics/external_validation_template.Rmd
include R code for data export in validation template to Erik L

# Estimate CI for AUC based on bootstrapping
# Use parallel processing to speed up the process
doParallel::registerDoParallel()
AUCci <- pROC::ci.auc(ROC, method = "bootstrap", boot.stratified = FALSE, parallel = TRUE)

# Check calibration. Note that devel should actually be "internal" for this example but I use
# "external", since that's what you will use for the UK data. 
calibration <- givitiR::givitiCalibrationBelt(obspred$obs, obspred$pred, devel = "external")
```

@@

>>>>

# Estimate CI for AUC based on bootstrapping
# Use parallel processing to speed up the process
doParallel::registerDoParallel()
AUCci <- 
  pROC::ci.auc(
    ROC, 
    method          = "bootstrap", 
    boot.stratified = FALSE, 
    parallel        = TRUE
  )

# Check calibration. Note that devel should actually be "internal" for this example but I use
# "external", since that's what you will use for the UK data. 
calibration <- 
  givitiR::givitiCalibrationBelt(
    obspred$obs, 
    obspred$pred, 
    devel = "external"
  )
```

@@

# Export data to Sweden

## ROC

If it would be OK to export coordinates for ROC-plots I would recommend this code to extract only the minimal data needed:

```{r}

roc_plot_coords <- 
  data.frame(
    specificities = ROC$specificities, 
    sensitivities = ROC$sensitivities
  )

roc3_plot_coords <- 
  data.frame(
    specificities = ROC3$specificities, 
    sensitivities = ROC3$sensitivities
  )

```

## AUC with CI

The text output from `AUCci` and `AUCci3` should be enough. Hence, the same character string that gets printed above (but now stored in an object).
```{r}
AUCci_print  <- capture.output(AUCci)
AUCci3_print <- capture.output(AUCci3)
```

## Export objects

Save objects above to file `export.RData` (in the current working directory).

```{r}
save(
  roc_plot_coords,
  roc3_plot_coords,
  AUCci_print,
  AUCci3_print,
  file = "export.RData"
)
```

## Calibration plots

### Help function

This is a simple help function to make a clean calibration belt plot and save it as TIFF (in the curent working directory):

```{r}
makeplot <- function(x, file_name = deparse(substitute(x))) {
  tiff(
    paste0(file_name, ".tiff"), 
    1024, 1024, pointsize = 36, 
    compression = "lzw"
  )

  tcks <- seq(.0, .1, .01)

  plot(
    x,
    xlim             = c(0, .06),
    ylim             = c(0, .08),
    xlab             = "Predicted probabilities [%]",
    ylab             = "Observed  probabilities [%]",
    main             = NULL,
    table            = FALSE,
    polynomialString = FALSE,
    pvalueString     = FALSE,
    nString          = FALSE,
    mar              = c(5, 4, 0, 0) + 0.1,
    xaxt             = "n",
    yaxt             = "n"
  )
  abline(v = .03, lty = "dashed", col = "darkgreen", lwd = 3)
  axis(1, at = tcks, lab = sprintf("%.0f", tcks * 100), las = TRUE)
  axis(2, at = tcks, lab = sprintf("%.0f", tcks * 100), las = TRUE)

  dev.off()
}
```
### Make and save figures

```{r}
makeplot(calibration)
makeplot(calibration3)
```

## ROC plots

If it not possible to export data for ROC-plot, here is some code to make a figure and save it as TIFF (in the current working directory) instead:

```{r}

roc_plot_coords %>% 
  ggplot(aes(1 - specificities, sensitivities)) +
  geom_path(size = 2) +
  geom_abline(intercept = 0, slope = 1, color = "grey", linetype = 2) +
  theme_minimal() +
  theme(
    legend.position = c(1, 0),
    legend.justification = c(1, 0),
    legend.title = element_blank()
  )

ggsave(
  "roc.tiff", 
  height = 10, 
  width = 10, 
  unit = "cm", 
  dpi = 900, 
  compression = "lzw"
)
```
